\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
%
\input{commands.tex}
\usepackage{rotating}
\usepackage{listings}
\usepackage{multirow}
%\usepackage{subcaption}
\usepackage[ampersand]{easylist}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{bm}
\usepackage{subcaption}
\usepackage[section]{placeins}
%
\begin{document}%
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{titlepage}
%
\PHnumber{ALICE-ANA-2018-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{D mesons in jets in \pPb\ collisions: preliminary figures for QM 2018}
\ShortTitle{D-jets in \pPb\ collisions: preliminary figures for QM 2018}   % appears on right page headers
%%% BASED ON THE QM2017 ANALYSIS NOTE ..... %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\author{Salvatore Aiola$^{1}$, Fabio F. Colamaria$^{2}$, Andrea Rossi$^{3}$, Antonio C. O. da Silva$^{4,5}$, Barbara A. Trzeciak$^{4}$}
\author{
1. Yale University, USA\\
2. University of Bari and INFN, Italy\\
3. University of Padova and INFN, Italy\\
4. Utrecht University, Netherlands\\
5. University of S\~ao Paulo, Brazil\\
}
\author{Email: barbara.antonina.trzeciak@cern.ch}
%
\ShortAuthor{ALICE Analysis Note 2018}      % appears on left page headers, do not change
%
\begin{abstract}
Open heavy flavors (D, B) are born from the fragmentation of heavy quarks ($c$, $b$) which are produced in hard scatterings possible only at the beginning of heavy-ion collisions. Minimal effects of Quark-Gluon Plasma (QGP) on the production of heavy quarks allow for a simpler theoretical description. Their negligible annihilation rate allows us to measure them and study their energy loss mechanism during their travel through the QGP. 
Upon colliding, partons in opposing high-energy beams can scatter violently to produce correlated showers of particles, or jets. These are expected to be modified by the interaction of the scattered partons with the surrounding QGP. Measuring D mesons in jets is therefore essential in understanding QGP.
A precise, quantitative understanding of charmed jets is unavailable in the framework of perturbative QCD (pQCD). Charm content is available from prompt production: ${\rm gg\, (q\bar{q})} \rightarrow {\rm c\bar{c}}$, 
%$gg(q\bar q)\rightarrow c\bar c$,
and from the parton shower of gluons and light quarks. %Charm hadrons coming from the fragmentation of prompt charm jets are expected to carry a larger fraction of the total jet momentum, as compared to those arising later in the parton shower. Therefore the measurement of charm jet fragmentation functions (FFs) can be used to estimate the relative strength of the two mechanisms.
The aim of the analysis is to extract the $p_T$ spectrum of the D-tagged jets. %both the $p_T$ spectrum of the D-tagged jets and the jet-$p_T$ fraction of the D mesons.
We identify D-meson candidates via their hadronic decay channels using topological selections and particle identification. These candidates are combined with the other charged tracks reconstructed by the central tracking system, using the anti-$k_T$ jet-finding algorithm. 
We extract the yield of D-tagged jets through their invariant mass analysis in bins of D $p_T$ and get their jet $p_T$ spectra. % and momentum fraction carried by the D meson. 
At the Quark Matter 2018, we show new preliminary results from the p-Pb analysis of the D$^0$-tagged jets, and \Dstar-tagged jets.

%The study of the charm content of jets is interesting because up to now it has eluded a precise quantitative understanding in the framework of perturbative QCD (pQCD). The charm content of jets is known to arise both from prompt production in the process ${\rm gg\, (q\bar{q})} \rightarrow {\rm c\bar{c}}$, and from the parton shower of gluons and light-flavor quarks. Charm hadrons coming from the fragmentation of prompt charm jets are expected to carry a larger fraction of the total jet momentum, as compared to those where the charm content arises later in the parton shower. Therefore the measurement of charm jet fragmentation functions (FFs) can be used to estimate the relative strength of the two mechanisms. Heavy-flavor jets can also provide important insights into the Quark-Gluon Plasma (QGP) produced in ultra-relativistic heavy-ion collisions, as heavy quarks are predicted to interact with the QGP differently compared to light quarks and gluons. The aim of the analysis is to extract both the $p_{\rm T}$ spectrum of the D-tagged jets and the jet-momentum fraction of the D mesons. We identify D-meson candidates via their hadronic decay channels using topological selections and particle identification. These D-meson candidates are combined with the other charged tracks reconstructed by the central tracking system, using the anti-$k_{\rm T}$ jet-finding algorithm. We extract the yield of D-tagged jets through an invariant mass analysis of the D-meson candidates associated with each jet, in bins of jet $p_{\rm T}$ and momentum fraction carried by the D meson. At the Strangeness in Quark Matter 2017 conference we show new preliminary results from the \pPb\ analysis. These results include solely th $p_{\rm T}$ spectrum of the D-tagged jets.
\end{abstract}
\end{titlepage}
%
\tableofcontents
\newpage
\input{content.tex}               %%%%%%%%%%% put the body of the article here

\end{document}
