\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
%
\input{commands.tex}
\usepackage{rotating}
\usepackage{float}
\usepackage{listings}
\usepackage{multirow}
%\usepackage{subcaption}
\usepackage[ampersand]{easylist}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{bm}
\usepackage{subcaption}
\usepackage[section]{placeins}
\usepackage{color}
%
\begin{document}%
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{titlepage}
%
\PHnumber{ALICE-ANA-2018-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{D mesons in jets in \pPb\ collisions: preliminary figures for QM 2018}
\ShortTitle{D-jets in \pPb\ collisions: preliminary figures for QM 2018}   % appears on right page headers
%%% BASED ON THE QM2017 ANALYSIS NOTE ..... %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\author{Salvatore Aiola$^{1}$, Fabio F. Colamaria$^{2}$, Andrea Rossi$^{3}$, Antonio C. O. da Silva$^{4,5}$, Barbara A. Trzeciak$^{4}$}
\author{
1. Yale University, USA\\
2. University of Bari and INFN, Italy\\
3. University of Padova and INFN, Italy\\
4. Utrecht University, Netherlands\\
5. University of S\~ao Paulo, Brazil\\
}
\author{Email: barbara.antonina.trzeciak@cern.ch}
%
\ShortAuthor{ALICE Analysis Note 2018}      % appears on left page headers, do not change
%
\begin{abstract}
Open heavy flavors (D, B) are born from the fragmentation of heavy quarks ($c$, $b$) which are produced in hard scatterings 
possible only at the beginning of heavy-ion collisions. Minimal effects of Quark-Gluon Plasma (QGP) on the production of heavy 
quarks allow for a simpler theoretical description. Their negligible annihilation rate allows us to measure them and study their energy loss mechanism during their travel through the QGP. 
Upon colliding, partons in opposing high-energy beams can scatter violently to produce correlated showers of particles, or jets. 
These are expected to be modified by the interaction of the scattered partons with the surrounding QGP. Measuring D mesons in jets is therefore essential in understanding QGP.
A precise, quantitative understanding of charmed jets is unavailable in the framework of perturbative QCD (pQCD). Charm 
content is available from prompt production: ${\rm gg\, (q\bar{q})} \rightarrow {\rm c\bar{c}}$, 
and from the parton shower of gluons and light quarks. 
The aim of the analysis is to extract the $p_T$ spectrum of the D-tagged jets. 
We identify D-meson candidates via their hadronic decay channels using topological selections and particle identification. These 
candidates are combined with the other charged tracks reconstructed by the central tracking system, using the anti-$k_T$ jet-finding algorithm. 
We extract the yield of D-tagged jets through their invariant mass analysis in bins of D $p_T$ and get their jet $p_T$ spectra.  
At the Quark Matter 2018, we show new preliminary results from the p-Pb analysis of the D$^0$-tagged jets, and \Dstar-tagged jets.
\end{abstract}
\end{titlepage}
%
\tableofcontents
\newpage
\input{content.tex}               %%%%%%%%%%% put the body of the article here

\end{document}
