\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
%
\input{commands.tex}
\usepackage{rotating}
\usepackage{float}
\usepackage{listings}
\usepackage{multirow}
%\usepackage{subcaption}
\usepackage[ampersand]{easylist}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{bm}
\usepackage{subcaption}
\usepackage[section]{placeins}
\usepackage{color}
\usepackage[toc,page]{appendix}
%
\begin{document}%
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{titlepage}
%
\PHnumber{ALICE-ANA-2018-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{\Dzero\ mesons in jets in \pp\ collisions: preliminary figures for HP 2018 (jet $p_{\text T}$ cross-section), SQM 2019 (parallel momentum fraction)}
\ShortTitle{\Dzero\ mesons in jets in \pp\ collisions: preliminary figures for HP 2018, SQM 2019}   % appears on right page headers
%%% BASED ON THE QM2017 ANALYSIS NOTE ..... %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\author{Auro Mohanty$^{1}$, Barbara A. Trzeciak$^{1}$, Andr\'e Mischke$^{1}$}
\author{
1. Utrecht University, the Netherlands\\
}
\author{Email: auro.mohanty@cern.ch, barbara.antonina.trzeciak@cern.ch, A.Mischke@uu.nl}
%
\ShortAuthor{ALICE Analysis Note 2018}      % appears on left page headers, do not change
%
\begin{abstract}
%The study of the charm content of jets is interesting because up to now it has eluded a precise quantitative understanding in the framework of perturbative QCD (pQCD).
%The charm content of jets is known to arise both from prompt production in the process ${\rm gg\, (q\bar{q})} \rightarrow {\rm c\bar{c}}$, and from the parton shower of gluons and light-flavor quarks.
%Charm hadrons coming from the fragmentation of prompt charm jets  are expected to carry a larger fraction of the total jet momentum, as compared to those where the charm content arises later in the parton shower. Therefore the measurement of charm jet fragmentation functions (FFs)  can be used to estimate the relative strength of the two mechanisms.
%Heavy-flavor jets can also provide important insights into the Quark-Gluon Plasma (QGP) produced in ultra-relativistic heavy-ion collisions, as heavy quarks are predicted to interact with the QGP differently compared to light quarks and gluons.

Heavy quarks (charm and beauty) are produced in hard parton scatterings in the early stages of hadronic collisions. Therefore, they are ideal probes to investigate the properties of the Quark-Gluon Plasma (QGP) produced in ultra-relativistic heavy-ion collisions. 
The measurement of heavy-flavour jets gives more direct access to the initial parton kinematics and can provide further constraints for heavy-quark energy loss mechanisms, in particular adding information on how the radiated energy is dissipated in the medium. It also allows us to characterize the heavy-quark fragmentation process and its possible modification in the hot nuclear matter environment. 
 
Studies in pp collisions are mandatory to characterize heavy quark production and fragmentation in vacuum, constituting the necessary reference for interpreting heavy-ion collision results. Differences between results from pp and p--Pb collisions can give insight on how the heavy-quark production and hadronization into jets is affected by cold nuclear matter effects.
 
The aim of the analysis is to present studies of the \Dzero-tagged jets in pp collisions at \s\ = 5.02 TeV. 
We identify D-meson candidates via their hadronic decay channels using topological selections and particle identification. These 
candidates are combined with the other charged tracks reconstructed by the central tracking system, using the anti-$k_T$ jet-finding algorithm. 
We extract the yield of D-tagged jets through their invariant mass analysis in bins of \Dzero\ $p_{\text T}$ and get their jet $p_{\text T}$ spectra or $z_{||}$ distribution.  \\
In this note, we present details of the \Dzero-tagged jet analysis approved as a preliminary result for the Hard Probes 2018 conference: \pt\ differential cross-section in \pp\ at \s\ = 5.02 TeV. The measurement was also be used as a baseline for the preliminary \Dzero-jet measureament in p-Pb collisions at \snn\ = 5.02 TeV, in order to extract the nuclear modification factor $R_{\text{pPb}}$. 
Also presented in this note are parallel momentum fraction ($z_{||, \text {ch}} = \frac{\vec p_{\text{ch jet}}.\vec p_{\text D}}{\vec p_{\text{ch jet}}.\vec p_{\text{ch jet}}}$) studies for different jet radii $R=$ 0.3, 0.4 in different intervals of jet $p_{\text T}$ aiming to be approved for Strangeness in Quark Matter 2019.
\end{abstract}
\end{titlepage}
%
\tableofcontents
%\newpage
\input{content.tex}               %%%%%%%%%%% put the body of the article here


%%%%%% Appendices %%%%%%%%%%%%%%
%\newpage
%\begin{appendices}
%\input{SysPbPbbinning}
%\end{appendices}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%           REFERENCES          %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{biblio}{}
\bibliographystyle{iopart-num}

%%%%%%%%%%%%
%%%%%%%%%%%%

\end{document}
